Template for indicator documentation

### 2023-09-28 functional_plant_indicators_natopen.Rmd
Shorten chapter name and list indicator names #77

# Functional plant indicators, naturally open ecosystems below the tree line (Grime's CSR values, Light, Nitrogen, Soil disturbance) {#Functional-plant-indicators-open}

@@

@@

>>>>

# Functional Plant Indicators - Naturally Open Ecosystems {#Functional-plant-indicators-open}

@@

Norwegian name: **Planteindikatorer**
<br />

@@

Indicators described in this chapter:

- Grime's CSR values
- Light
- Nitrogen
- Soil disturbance

### 2023-09-28 functional_plant_indicators_seminat.Rmd
Shorten chapter name and list indicator names #77

# Functional plant indicators, semi-natural ecosystems (Light, Moisture, pH, Nitrogen, Phosphorus, Grazing_mowing, Soil disturbance) {#Functional-plant-indicators-seminat}

@@

>>>>

# Functional Plant Indicators - Semi-Natural Ecosystems {#Functional-plant-indicators-seminat}

<br />
Norwegian name: **Planteindikatorer**
<br />

@@

Indicators described in this chapter:

- Light
- Moisture
- pH
- Nitrogen
- Phosphorus
- Grazing_mowing
- Soil disturbance
